	\documentclass[a4paper,14pt]{extreport}
\usepackage{pgf-pie}  

	\begin{document}
	\begin{table}[]
	\begin{tabular}{l|l c r|l}
	 
	        & $a_{1,1}$ & $\dots, a_{1,n}$ & 0 &                 \\  
	        & $a_{1,1}$ & $\dots, a_{1,n}$ & 0 &                 \\ 
	        & \multicolumn{3}{l|}{\dotfill}   &                  \\  
	        & $a_{1,1}$ & $\dots, a_{1,n}$ & 0 &                 \\ 
	$d_{n+1}$ &         &                &   & = $\pm 2ad_n$ = 0 \\  
	        & $a_{1,1}$ & $\dots, a_{1,n}$ & 0 &                 \\  
	        & $a_{1,1}$ & $\dots, a_{1,n}$ & 0 &                 \\ 
	        & \multicolumn{3}{l|}{\dotfill}   &                  \\ 
	        & $a_{1,1}$ & $\dots, a_{1,n}$ & 0 &                 \\ 
	\end{tabular}
	\end{table}

 

 

\begin{tikzpicture}
\pie{22.97/Los Angeles Lakers,
22.97/Boston Celtics,
8.11/Golden State Warriors,
8.11/Chicago Bulls,
6.76/San Antonio Spurs,
31.07/Other Teams}
\end{tikzpicture}

 

\end{document}
              Speak on the main advantages of modern technology.

1. AI 
frequent expressions that "The human has not to think anymore because artificial intelligence will be able to think that what to do and how to do it." this is generally not true since artificial intelligence is most often used for a specific task. Have you ever seen an AI that can draw and drive and play chess. for example, take the artificial intelligence in the Tesla Ilona Mask car, it was created only to drive cars, it can be converted to some other task, but it was created only to safely drive a car, park, and so on.


2. Technology for Disabled People to Make Them Able 
Technology makes everything possible nearly. Artificial hands and feet are invented recently for people who have some kind of disabilities of hands and feet.
By using these artificial hands and feet they become able to use hands properly and walk properly.
There are a lot more devices invented which are used by different people who have some kind of disabilities.  


3. Technology Solar Electrical Power
Solar power is the new invention of today’s world. There are devices and machines which convert the sun’s heat and light to electrical energy. Solar power technology is a new kind of technology that is pollution-free. It does not produce any kind of pollution as other technological machines produce pollution when used. (Like electrical generator). This is one of the best benefits of Solar power technology in that it doesn’t damage our environment.  Solar power technology is very famous nowadays, it is used in different areas.... It is used in motor cars, street lights, hand torch, buildings, homes, and factories, etc. to produced electrical energy from the sunlight.

Technology Easy Access to Information

4. Technology use for Education
 there is no such field in which technology is not used.
Technology also plays a very important role in the field of education, it has a lot of advantages for the students and as well as for the teachers.
Technology makes study and teaching very easy for students and teachers.
There is a lot of electronic devices, gadgets, and software that help a lot of students in education.
For example: Nowadays the multimedia projector is used in every education system. It makes teaching very easy and interesting for the teacher.
They can use the multimedia projector to present the knowledge to the students in a better way.
Students get motivated and take an interest in learning.
To study more about technology use in education,
























